### 2020-06-22 response/response-demography-3.tex

\section*{Deputy Editor}

\begin{enumerate}

\item The overall topic and research question is not clear in the
introduction. The main topic relates to changes in birth spacing over
time, which are influenced by sex selection/sex composition and maternal
education, and how this affects fertility and infant mortality. This is
a long list of interesting questions and analyses but this is confusing
for the reader. It would be useful to have a succinct statement about
what the study is about (what are key independent variables/concepts and
key outcomes) and place that in the introduction and before the data and
analyses section. This way, the reader can understand why the analyses
will proceed in a particular order and what is being tested. In
addition, the titles of the figures and tables should be reviewed to see
if they could better reflect the analyses undertaken. Overall, the
reader needs to be reminded at the beginning and in each section what
you aim to do.

[Response:] I have rewritten the Introduction to emphasize the main question I address
(``how did birth spacing respond to these changes, especially the introduction and spread 
of sex selection?'') and the two associated questions addressing the effects of changes in 
birth spacing (``to what extent do changes in birth spacing bias our standard fertility 
estimates?'' and `` how do the changes in birth spacing and the increased use of abortions 
impact children's chances of survival?'').

### 2020-06-23 paper/sex_selection_spacing-ver4.tex
Add key independent variables/concepts and outcomes
- Clarify hazard model set-up
- Add main outcomes and "explanatory" variables
- Explain fertility comparison
- Discuss infant mortality model

% How the study progresses
To investigate how birth spacing has changed over time and across groups with the introduction 
of sex selection, I apply a competing risk hazard model to the birth histories of Hindu 
women, covering the period 1972 to 2016, using data from the four National Family and 
Health Surveys (NFHS).
The model directly incorporates the effects of sex-selective abortions on birth intervals
and the likelihood of a son, but it also works with no sex selection.
The empirical model allows me to predict fertility, taking into
account both the likelihood of parity progression and the likelihood of having a child of 
a specific sex.

I use the same data to examine how infant mortality risk has changed with the changing 
birth spacing and whether sex selection affects infant mortality.

>>>>

% How the study progresses
To investigate how birth spacing has changed over time and across groups with the 
introduction of sex selection, I use a competing risk hazard model with two exit 
states: the birth of a girl or the birth of a boy. 
I apply the model to the birth histories of Hindu women covering 1972 to 2016 using 
data from the four National Family and Health Surveys (NFHS).

The primary outcomes I examine are average birth intervals, the sex ratio of births, 
and the likelihood of a next birth. 
Because sex selection might affect the distribution of birth intervals, I also
examine the 25th and 75th percentiles of birth intervals. 
I estimate the model across four periods to capture the changing access and 
legality of sex selection. 
The key explanatory variables are maternal education, the sex composition of previous 
children, and area of residence.

The empirical model allows me to predict cohort fertility. 
To examine to what extent tempo effects bias our standard fertility measures, I compare 
this predicted cohort fertility with fertility calculated from age-specific fertility rates.

I use the same data to study how infant mortality risk has changed with the changing 
birth spacing and whether sex selection directly affects infant mortality. 
The explanatory variables are the same as for the spacing analysis, except for the 
addition of birth spacing and index child sex.
